Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-22 plosOne/SI/S1glossary.tex
revisados SIs

@@

The subjects involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should help readers as a concise references.

@@

      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and proving dedication \\\hline

>>>>

\usepackage{nameref,hyperref}
\usepackage{xcolor}       
\hypersetup{
        colorlinks,
        linkcolor={red!50!black},
        citecolor={blue!50!black},
        urlcolor={blue!80!black}
}

@@

The knowledge fields involved in this article have numerous jargons, acronyms and abbreviations. Table~\ref{tab:glos} should assist readers as a concise reference.

@@

      \aan  & Algorithmic Autoregulation & a platform for personal transparency, sharing ongoing work and demonstration of dedication \\\hline
